\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-22 pldi/draft.tex
Half-way pass over eval

@@

\TODO{Remember to mention that deathstar has 128 threads but 64
  cores. So it is reasonable for the speedup to not go further in cpu
  heavy pipelines.}

\TODO{Should we mention that we empirically show that pash produces
  correct code?}

% FIXME
% \kk{We should make sure to measure the time that it takes for the
%   whole process to run (parsing, translating, optimizing, planning)
%   together with the scripts. This will probably be negligible, but we
%   still have to mention it. }
% 
% \kk{Also, we have to have one-two handcrafted examples that have more
%   than one pipeline, to show the execution time end to end, as this
%   cannot be shown with the one-pipeline examples since they only have
%   one graph, so no back and forth between shell and dish.}
% 
% \kk{Furthermore it would be great to have one distributed example that
%   runs in more than one node (if we have time)}
% 
% \kk{Also we have to make sure to measure with and without the final
%   cat of output file, so that we show that this is also negligible.}
% 
% \kk{We have to make sure that we repeat that the results are the same
%   in all tests that we run. Corectness, blah blah ...}
% 
% \kk{We should have at least some pipelines that have a bad pure
%   command in them.}

\begin{table*}[t]
\center
\footnotesize
% \setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Summary of shell one-liners}.
    The shell one-liners are small pipelines (\ie ones developed on-the-fly) drawn from various sources and applied to large datasets.
  }
}
%% \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} llllll}
%% \toprule
%%   Script                 ~&~ Structure                    & Input (MB)& Time (Seq)    & Script Size (LoC)             & Highlights                                        \\
%% \midrule
%% % https://github.com/andromeda/sdsh/blob/master/scripts/grep.sh
%%   \tti{grep}         ~&~$3\times$\tsta                & 1000      &  78m 36.77s   &   30\qquad 134\qquad  1304    & complex NFA regex                                 \\
%% % https://github.com/andromeda/sdsh/blob/master/scripts/minimal5.sh
%%   \tti{sort}         ~&~~$\tsta, \tpur$               & 10000     &  23m 19.85s   &   33\qquad 129\qquad  1209    & \tti{sort}ing                                     \\
%% % https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
%%   \tti{wf}               ~&~~$3\times\tsta, 3\times\tpur$ & 1000      &   2m 11.18s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
%% % https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
%%   \tti{top-n}            ~&~~$2\times\tsta, 4\times\tpur$ & 1000      &   6m 53.55s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
%% % https://github.com/andromeda/sdsh/blob/master/scripts/ngrams.sh
%%   \tr{\tti{bi-gram}          ~&~~$2\times\tsta, 4\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & stream shifting and merging                       \\}
%% % https://github.com/andromeda/sdsh/blob/master/scripts/spell.sh
%%   \tti{spell}            ~&~~$4\times\tsta, 3\times\tpur$ & 1000      &   8m 13.42s   &  37 \qquad 257\qquad  2417    & comparisons (\tti{comm})                          \\
%% % https://github.com/andromeda/sdsh/blob/master/scripts/diff.sh
%%   \tr{\tti{diff}             ~&~~$4\times\tsta, 3\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & shuffling and non-distributable \tti{diff}ing     \\}
%%   \tti{shortest-scripts} ~&~~$5\times\tsta, 2\times\tpur$ & 8.6       &   2m 50.03s   &  61 \qquad 253\qquad  2413    & extensive file-system operation   \\
%% \bottomrule
%% \end{tabular*}
\input{microbenchmarks-table}
\label{tab:eval}
\end{table*}

\kk{Maximum scaleup for both diff and set-diff is around half because
  they already have two sorts running in parallel (as diff, and comm
  take two inputs).}

@@

\TODO{(Maybe) we need to mention that eager has disk usage overhead
  that is linear to the size of the pipeline and the size of the
  input.}

At a high level, we are interested in understanding whether \sys can indeed scale pipelines out automatically and correctly.
To achieve this, we use six micro-benchmarks and one macro-benchmark, collected primarily from prior literature.

Micro-bench\-marks~\sx{ours} are one-off, simple one-liners that take a few seconds to write;
  such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
These pipelines are taken from real use cases~\cite{bentley1985spelling, bentley1986literate, taylor2004wicked} and, precisely due to their small size, highlight stress on a handful of stages.

The complex macro-benchmark (\S\ref{macro1}) is designed to handle realistic workloads by today's standards.
It is about an order of magnitude larger than the micro-benchmarks, but its perceived lack of complexity is deceiving:
  as shown, if written in a conventional language it would correspond to a program on the order of hundreds of lines of code.

Several results are worth highlighting.
First, programs see a significant speedup, often more $10\times$ over sequential execution  while returning identical results (on very large datasets).
\sys's transformation and planning phase take around 50--300ms, negligible ($<$2\%) for short-running pipelines and virtually non-existent for long-running ones.
As \sys rewrites to highly-optimized shell primitives rather than using a managed language runtime, it always has a COST~\cite{mcsherryscalability} of 2.
Finally, \sys preserves the productivity of the shell:
  the equivalent program for a small part of the macro-benchmark pipeline requires over a 150 lines of code in combined Java and Bash to run distributed on top of Hadoop.
  %% in another, the program expressed by the pipeline was the subject of a semester project in a graduate course on distributed systems~\cite{blinded} where student implementations ranged between 1--3\textbf{K} lines of code.

Experiments were run on a %\todo{network of five workstations} connected by 1Gbps links: 
  machine with 512GB of memory and 128 virtual (64 physical) $\times$ 2.1GHz Intel Xeon E5-2683 cores.
%\todo{four smaller machines (\wkq), each with 4GB of memory and two 3.33GHz Intel Core Duo E8600 processors}.
For our software setup, we use Debian 4.9.144-3.1, GNU Core-utils 8.30-3, GNU Bash 5.0.3(1)-, Python 3.7.3, and OCaml 4.05.0.
Generally, no special configuration was made in hardware or software.
All pipelines are set to (initially) read from and (finally) write to the file-system (except as otherwise stated).
Whenever \ttt{curl} is part of a pipeline, it fetches data from a different physical host on the same network connected by 1Gbps links.
A more detailed description of the setup and experiments, including reproducible scripts, is included in the accompanying (anonymized) online repository.

@@

The goal of this subsection is to evaluate \sys on popular, common, or classic \unix pipeline patterns.

@@

%% \begin{figure*}[t]
%%     \centering
%%     %% \subcaptionbox{\label{eval:minimal_grep}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:grep}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:minimal_sort}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:topn}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:wf}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
%%     %% }
%%     %% \subcaptionbox{\label{eval:spell}}{
%%     %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
%%     %% }
%%     %% \caption{a}
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_grep}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/spell_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:grep}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_sort}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%       \centering
%%       \includegraphics[width=\textwidth]{\detokenize{./figs/set-diff_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_sort}
%%     \end{subfigure}%

%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:topn}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:wf}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%         \centering
%%         \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:spell}
%%     \end{subfigure}%
%%     ~
%%     \begin{subfigure}[b]{0.24\textwidth}
%%       \centering
%%       \includegraphics[width=\textwidth]{\detokenize{./figs/bigrams_throughput_scaleup.pdf}}
%%         %% \caption{TODO}
%%         %% \label{eval:minimal_sort}
%%     \end{subfigure}%
%%     \caption{
%%       \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
%%       Four different configurations per benchmark:
%%       (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
%%       (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
%%       (ii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
%%       (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
%%       (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
%%       \nv{Maybe it makes sense to show log x-axis?}
%%       \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
%%     }
%%     \vspace{-15pt}
%%     \label{fig:microbenchmarks}
%% \end{figure*}

\heading{Programs}

\kk{How can we include a result for grep-light?  This is the IO
  intensive CPU-light grep. \sys has no speedup but also no slowdown
  (even if it IO heavy). Should we just mention that in text in
  passing?}

\kk{Remember to mention that for spell and bigrams we dont show other
  parallel because they are all close to 1 (no speedup).}

Tab.~\ref{tab:eval} summarizes the collection of micro-benchmarks used to evaluate \sys.
Benchmark names (col. 1) correspond to the names on the plots (Fig.~\ref{fig:microbenchmarks}), and structure (col. 2) summarizes the different classes of commands used in the script.
% The centralized pipelines read files of various sizes from disk and write to disk.
Input sizes and times (col. 3, 4) summarize the characteristics of the largest sequential executions. % (200 files in Fig.~\ref{fig:microbenchmarks}).
Script sizes (col. 5) report on \sys's rewritten output for three different distribution sizes---$1\times$, 10$\times$, and $100\times$.
Size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
The first number alone is interesting, as it captures \sys's output for the sequential script.
As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% this is the size of 
This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
FIFOs are simply pipes made explicit;
  the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

In more detail, \ttt{grep} is a short script centered around an expensive \tsta command;
% a DFA-based regular expression matching phase;
  while the \unix \ttt{grep} command defaults to a Thompson NFA, this particular expression makes use of DFA-based backtracking patterns resulting in high runtime overhead.
The \ttt{sort} pipeline is equally short, but its central operation is a command in \pur.
The next two benchmarks, \ttt{wf} and \ttt{top-n}, are based on McIlroy's now classic word-counting program~\cite{bentley1986literate};
  they use sorting, rather than tabulation, to identify high-frequency terms in a corpus.
% \tr{The \ttt{bi-gram} pipeline calculates n-grams of base two;
%   it makes clever use of \ttt{tail} to shift a stream by one word and \ttt{paste} to fuse (zip) two streams together.}
The next pipeline is based on the original \ttt{spell} program developed by Johnson~\cite{bentley1985spelling}---another \unix classic:
  after some preprocessing, it makes clever use of \ttt{comm} to report words not in the dictionary.
Finally, \ttt{shortest-scripts} is a pipeline~\cite[pg. 7]{taylor2004wicked}that identifies the 15 shortest shell scripts in the user's \ttt{PATH};
   interestingly, it uses the \ttt{file} utility and a higher-order \ttt{wc} via \ttt{xargs}.

\heading{Performance}
% TODO \nv{Need to change terminology in plots---files should be (attempted) parallelism, name benchmark, cat should be merge.}
Fig.~\ref{fig:microbenchmarks} presents the speedup gained by \sys as a function of the level of parallelism (1--200$\times$).
% we experiment with a $200\times$ level of parallelism to see potential overheads
Each one of these plots reports on three different configurations:
  (i) distributed, which captures only the runtime of the distributed computation,
  (ii) +compile, which adds the \sys' analysis and generation overhead, and
  (iii) +merge, which adds a final merger  gathering the results at the end of the pipeline.
Parallelism of 200$\times$ was explicitly chosen to show the \sys-internal overheads on suboptimal configurations;
  \sys itself would never attempt a factor that is above the number of available compute nodes.
The results show significant speedups, ranging between 4--70$\times$, depending on the parallelizability characteristics of individual pipelines.

@@

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{
	  \textbf{Speedup (left axis) and over sequential execution (right axis) for all Unix50 pipelines.}
		Parallelism is 16$\times$ on 10GB of input data~\cf{unix50}.
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}

>>>>

\begin{table*}[t]
\center
\footnotesize
% \setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Summary of shell one-liners}.
    Small pipelines (\ie ones usually developed on-the-fly) drawn from various sources and applied to large datasets.
    % Names correspond to the speedup plots (Fig.~\ref{fig:microbenchmarks}).
    Structure summarizes the different classes of commands used in the script.
    Input and seq. time report on the input size fed to the script and the timing of its sequential execution.
    Nodes and compile time report on \sys's resulting \todo{AST} size and compilation time for two indicative parallelization configurations.
    % Highlights notes a few key features of each script.
  }
}
\input{microbenchmarks-table}
\label{tab:eval}
\end{table*}

@@

%> \TODO{Remember to mention that deathstar has 128 threads but 64
%>   cores. So it is reasonable for the speedup to not go further in cpu
%>   heavy pipelines.}
%> 
%> \TODO{Should we mention that we empirically show that pash produces
%>   correct code?}
%> 
% FIXME
% \kk{We should make sure to measure the time that it takes for the
%   whole process to run (parsing, translating, optimizing, planning)
%   together with the scripts. This will probably be negligible, but we
%   still have to mention it. }
% 
% \kk{Also, we have to have one-two handcrafted examples that have more
%   than one pipeline, to show the execution time end to end, as this
%   cannot be shown with the one-pipeline examples since they only have
%   one graph, so no back and forth between shell and dish.}
% 
% \kk{Furthermore it would be great to have one distributed example that
%   runs in more than one node (if we have time)}
% 
% \kk{Also we have to make sure to measure with and without the final
%   cat of output file, so that we show that this is also negligible.}
% 
% \kk{We have to make sure that we repeat that the results are the same
%   in all tests that we run. Corectness, blah blah ...}
% 
% \kk{We should have at least some pipelines that have a bad pure
%   command in them.}

%>\kk{Maximum scaleup for both diff and set-diff is around half because
%>  they already have two sorts running in parallel (as diff, and comm
%>  take two inputs).}

@@

%> \TODO{(Maybe) we need to mention that eager has disk usage overhead that is linear to the size of the pipeline and the size of the input.}

At a high level, we are interested in understanding whether \sys can indeed scale shell scripts out automatically and correctly.
To answer this question, we use several scripts collected out from the wild, along with a few micro-benchmarks for targeted comparisons.

% Micro-bench\-marks~\sx{ours} are one-off, simple one-liners that take a few seconds to write;
%   such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
% These pipelines are taken from real use cases~\cite{bentley1985spelling, bentley1986literate, taylor2004wicked} and, precisely due to their small size, highlight stress on a handful of stages.
% The complex macro-benchmark (\S\ref{macro1}) is designed to handle realistic workloads by today's standards.
% It is about an order of magnitude larger than the micro-benchmarks, but its perceived lack of complexity is deceiving:
%   as shown, if written in a conventional language it would correspond to a program on the order of hundreds of lines of code.

\heading{Highlights}
\fixme{
Scripts see a significant speedup, often up to $10\times$ over sequential execution while returning identical results (on very large datasets).
\sys's transformation and planning phase take around 50--300ms, negligible ($<$2\%) for short-running pipelines and virtually non-existent for long-running ones.
As \sys rewrites to highly-optimized shell primitives rather than using a managed language runtime, it always has a COST~\cite{mcsherryscalability} of 2.
Finally, \sys preserves the productivity of the shell:
  the equivalent program for a small part of the macro-benchmark pipeline requires over a 150 lines of code in combined Java and Bash to run distributed on top of Hadoop.
}
  %% in another, the program expressed by the pipeline was the subject of a semester project in a graduate course on distributed systems~\cite{blinded} where student implementations ranged between 1--3\textbf{K} lines of code.

\heading{Setup}
Measurements were taken on a machine with 512GB of memory and 64 physical $\times$ 2.1GHz Intel Xeon E5-2683 cores running Debian 4.9.144-3.1, GNU Core-utils 8.30-3, GNU Bash 5.0.3(1)-, Python 3.7.3, and OCaml 4.05.0.
No special configuration was made in hardware or software.
Except as otherwise noted,
  (i) all pipelines are set to (initially) read from and (finally) write to the file-system,
  (ii) \ttt{curl} fetches data from a different physical host on the same network connected by 1Gbps links.
% A more detailed description of the setup and experiments, including reproducible scripts, is included in the accompanying (anonymized) online repository.

@@

The goal of this subsection is to evaluate \sys on popular, common, or classic \unix pipeline patterns~\cite{bentley1985spelling, bentley1986literate, taylor2004wicked}.

@@

\heading{Programs}
%>\kk{How can we include a result for grep-light?  This is the IO
%>  intensive CPU-light grep. \sys has no speedup but also no slowdown
%>  (even if it IO heavy). Should we just mention that in text in
%>  passing?}
%>
%>\kk{Remember to mention that for spell and bigrams we dont show other
%>  parallel because they are all close to 1 (no speedup).}
Tab.~\ref{tab:eval} summarizes the collection of programs shown in Fig.~\ref{fig:microbenchmarks}, which in turn reports on their performance characteristics.
Grep and Grep-light are in \sta, with the former centered around an expensive DFA-based backtracking expression.
% a DFA-based regular expression matching phase;
 % while the \unix \ttt{grep} command defaults to a Thompson NFA, this particular expression makes use of DFA-based backtracking patterns resulting in high runtime overhead.
Sort is a short script centered around a \pur command.
Wf and Top-n are based on McIlroy's classic word-counting program~\cite{bentley1986literate};
  they use sorting, rather than tabulation, to identify high-frequency terms in a corpus.
% \tr{The \ttt{bi-gram} pipeline calculates n-grams of base two;
%   it makes clever use of \ttt{tail} to shift a stream by one word and \ttt{paste} to fuse (zip) two streams together.}
Spell, based on the original \ttt{spell} developed by Johnson~\cite{bentley1985spelling}, is another \unix classic:
  after some preprocessing, it makes clever use of \ttt{comm} to report words not in a dictionary.
Shortest-scripts extracts the 15 shortest scripts in the user's \ttt{PATH}, using the \ttt{file} utility and a higher-order \ttt{wc} via \ttt{xargs}~\cite[pg. 7]{taylor2004wicked}.
Diff and Set-diff compare streams via a \ttt{diff} (in \npu, non-parallelizable) and \ttt{comm} (in \pur), respectively.
Sort-sort uses consecutive \pur commands without interleaving them with a \pur that has the effect of significantly condensing the input size (\eg \ttt{uniq}).
The two \ttt{bi-grams} replicate and shift a stream by one entry to calculate bigrams over the input; the \ttt{optimized} version \todo{has a difference}.

\heading{Results}
% TODO \nv{Need to change terminology in plots---files should be (attempted) parallelism, name benchmark, cat should be merge.}
Fig.~\ref{fig:microbenchmarks} presents the speedup gained by \sys as a function of the level of parallelism (2--64$\times$).
% we experiment with a $200\times$ level of parallelism to see potential overheads

In Tab.~\ref{tab:eval} contains two benchmarks that are not shown in Fig.~\ref{fig:microbenchmarks}, as they are artificial modifications intended to highlight \sys-internal characteristics and not lead to a speedup.
  \todo{highlight 2--3 results on things that were not shown in Fig.7}
%   size grows due to the resulting complexity of coordinating among parallel executions---multiple FIFOs per pipeline stage, merging and splitting, encoding of divide-and-conquer synchronization \etc
% The first number alone is interesting, as it captures \sys's output for the sequential script.
% As there is no parallelism involved, it highlights the initial (bare minimum) cost corresponding to using \sys.
% % this is the size of 
% This change in size does not necessarily translate to observed runtime, as most of the size increase comes from the setup and teardown of FIFOs responsible for interprocess (IPC) communication.
% FIFOs are simply pipes made explicit;
%   the performance characteristics, including in-kernel buffering and synchronization mechanisms, are identical between the two.

@@

\heading{Take-aways}
\sys achieves significant speedups that range between 4--60$\times$ depending on the parallelizability characteristics of the commands used.
\sys's runtime constructs offer significant improvements over the baseline speedup achieved by \sys's core transformations.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.80\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{
	  \textbf{Unix50 scripts.}
    Speedup (left axis) over sequential execution (right axis) for Unix50 scripts.
		Parallelism is 16$\times$ on 10GB of input data~\cf{unix50}.
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}
